Papers

### 2025-09-26 index.qmd
add new paper info

>>>>

<font color="#d08770">[September 26 2024].</font> **Paper accepted**. Hussain M, Foglia SD, Park J, Ramdeo KR, Adams FC, Drapeau CC, Bobinski AR, Carter MJ, & Nelson AJ. Ipsilateral contraction increases map area and decreases motor threshold for contralateral hand muscle. *Neuroscience*. [https://doi.org/10.1016/j.neuroscience.2025.09.034](https://doi.org/10.1016/j.neuroscience.2025.09.034){target="_blank"}

### 2025-09-26 papers.qmd
add new paper info

>>>>

- Hussain M., Foglia SD., Park J., Ramdeo KR., Adams FC., Drapeau CC., Bobinski AR., Carter MJ., & Nelson AJ. Ipsilateral contraction increases map area and decreases motor threshold for contralateral hand muscle. *Neuroscience*. ---
[{{< ai doi >}}](https://doi.org/10.1016/j.neuroscience.2025.09.034){target="_blank" style="color: inherit;"}
[{{< fa file-pdf >}}](https://raw.github.com/cartermaclab/carterlab-papers/main/2025_hussain-etal_ipsilateral-contraction-increases-map-area-and-decreases-motor-threshold-for-contralateral-hand-muscle.pdf){target="_blank" style="color: inherit;"}
